Elephace: Elephant Re-identification Using Deep Learning

### 2022-05-05 Report/PaperForReview.tex
updates: tables

\section{Experiments and Results}
\label{sec:expresults}
Number of experiments were performed on all three model. The Table1 shows parameters tried for each of the models.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{ c | c | c} 
      \textbf{Classification} & \textbf{Few Shot} & \textbf{Siamese}\\
      \hline
      \makecell{RestNet50,  \\ InceptionV3} & \makecell{ RestNet50, \\ InceptionV3} & \makecell{RestNet50, \\ InceptionV3 }\\
       \hline
      \makecell{Image \\ Augmentation}  & \makecell{Image \\Augmentation} & \makecell{Image \\ Augmentation}\\
      \hline
      Finetuning  & Finetuning & Embedding size\\
      \hline
        & Support set size & Triplet loss margin\\
     \hline
     	& & Triplet loss strategy\\
     \hline
	& & \makecell{Optimizer: \\ Adam, SGD}\\
     \hline
      	& & Aspect Ratio\\
    \end{tabular}
  \caption{Model Experiments}
  \label{tab:table1}
  \end{center}
\end{table}

@@

For elephant classification model, we used two backbone models of ResNet50 and InceptionV3. We found that both the model performed well on zoo elephants dataset with top-1 accuracies of 0.9971 and 0.979 respectively. This model did not perform well on wild dataset with top-1 accuracies of 0.21 and 0.16 respectively. The top-1, 3, and 5 accuracies for both zoo and wild dataset are shown in Table 2

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{ c | c | c | c} 
    \textbf{Classification} & \textbf{Few Shot} & \textbf{Siamese}\\

    \hline
    \multicolumn{3}{c}{Multi-column}& \\
    \cline{1-3}
    X&X&X\\
    X&X&X\\
    \hline

\end{tabular}
  \caption{Elephant Classifier Zoo and Wild Dataset Accuracies}
  \label{tab:table 2}
  \end{center}
\end{table}

@@

>>>>

\section{Experiments and Results}
\label{sec:expresults}

@@

For elephant classification model, we used two backbone models of ResNet50 and InceptionV3. We found that both the model performed well on zoo elephants dataset with top-1 accuracies of 0.9971 and 0.979 respectively. This model did not perform well on wild dataset with top-1 accuracies of 0.21 and 0.16 respectively. The top-1, 3, and 5 accuracies for both zoo and wild dataset are shown in Table \ref{tab:clf-results}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\begin{tabular}{@{}lllllll@{}}
\toprule
                                 & \multicolumn{3}{l}{Zoo Elephants}          & \multicolumn{3}{l}{Wild Elephants} \\ \midrule
\multicolumn{1}{l|}{}            & top-1 & top-3 & \multicolumn{1}{l|}{top-5} & top-1      & top-3     & top-5     \\
\multicolumn{1}{l|}{ResNet50}    & 0.997 & 0.997 & \multicolumn{1}{l|}{0.997} & 0.210      & 0.325     & 0.383     \\
\multicolumn{1}{l|}{InceptionV3} & 0.979 & 0.991 & \multicolumn{1}{l|}{0.994} & 0.159      & 0.243     & 0.272     \\ \bottomrule
\end{tabular}
\caption{Accuracy results on Zoo and Wild elephants datasets using Classification for re-identification}
\label{tab:clf-results}
\end{table}

@@

\begin{table}[]
\begin{tabular}{@{}lllllll@{}}
\toprule
                       & \multicolumn{3}{l}{ResNet50}               & \multicolumn{3}{l}{InceptionV3} \\ \midrule
\multicolumn{1}{l|}{n} & top-1 & top-3 & \multicolumn{1}{l|}{top-5} & top-1     & top-3    & top-5    \\
\multicolumn{1}{l|}{1} & 0.439 & 0.572 & \multicolumn{1}{l|}{0.703} & 0.449     & 0.585    & 0.659    \\
\multicolumn{1}{l|}{3} & 0.776 & 0.9   & \multicolumn{1}{l|}{0.943} & 0.810     & 0.923    & 0.959    \\
\multicolumn{1}{l|}{5} & 0.852 & 0.928 & \multicolumn{1}{l|}{0.955} & 0.918     & 0.966    & 0.976    \\
\multicolumn{1}{l|}{7} & 0.931 & 0.978 & \multicolumn{1}{l|}{0.989} & 0.991     & 0.995    & 0.995    \\
\multicolumn{1}{l|}{9} & 0.953 & 0.985 & \multicolumn{1}{l|}{0.992} & 0.998     & 0.998    & 0.993   
\end{tabular}
\caption{Accuracy results on Zoo elephants datasets using Few Shot for re-identification}
\label{tab:few-shot-results}
\end{table}
